---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("fooof_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->

Load data

```{rave load_rave_subject, use_rave = TRUE, export = "subject", format = "rave-subject"}
subject = raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

```{rave load_rave_repository, use_rave = TRUE, export = "repository", format = "rave_prepare_subject_voltage_with_epoch", cue = "always"}
repository = raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = channels_to_load,
  epoch_name = epoch_name,
  reference_name = reference_name,
  time_windows = time_window_to_load,
)
```

```{rave get_data_sampling_rate, use_rate = TRUE, export = "sample_rate"}
sample_rate <- repository$subject$raw_sample_rates[[1]]
```

```{rave prepare_data_for_fooof, use_rave = TRUE, deps = "repository", export = "data_for_fooof"}
data_for_fooof = list(
  sample_rate = repository$subject$raw_sample_rates,
  electrodes = repository$electrode_list,
  analyze_channel = analyze_channel,
  epoch_table = repository$epoch_table,
  condition_groupings = unname(condition_groupings),
  voltage = repository$voltage$data_list[[sprintf("e_%d", analyze_channel)]]
)
```

```{rave prepare_trial_subset, use_rave = TRUE, deps = c("repository", "condition_groupings"), export = "subset_analyzed"}
process_data <- function(repository, conditions_analyzed) {
  # Apply the condition to filter rows
  trial_selection <- repository$epoch_table$Condition %in% conditions_analyzed
  sub_volt <- subset(repository$voltage$data_list$e_14, Trial ~ trial_selection)

  # Calculate the mean across the first two dimensions
  matrix_volt <- apply(sub_volt, c(1, 2), mean)

  # Convert the matrix to a dataframe
  df_volt <- as.data.frame(matrix_volt)

  # Set column names for trials as they appear in the original array
  colnames(df_volt) <- dimnames(sub_volt)$Trial

  # Add 'Time' as a new column in the dataframe
  df_volt$Time <- as.numeric(dimnames(sub_volt)$Time)

  # Rearrange the dataframe to have 'Time' as the first column
  subset_analyzed <- df_volt[c("Time", dimnames(sub_volt)$Trial)]

  # Return the processed DataFrame
  return(subset_analyzed)
}
conditions_analyzed <- condition_groupings[['1']][['conditions']]
subset_analyzed <- process_data(repository=repository, conditions_analyzed=conditions_analyzed)


```


```{r}
# repository$voltage$data_list$e_14
```


```{python}
subset_analyzed = r.subset_analyzed
sample_rate = r.sample_rate
window_length = r.window_length
freq_range = r.freq_range
max_n_peaks = r.max_n_peaks
```


```{python generate_power_outputs, use_rave = TRUE, deps = c("subset_analyzed", "sample_rate", "window_length", "freq_range"), export = "power_outputs"}
# Parameters for preprocessing (you should adjust these based on your actual requirements)
fs = sample_rate

# Number of timepoints = sample rate * window size in sec
nperseg = sample_rate * window_length

freq_range = freq_range

power_outputs = shared.preprocess_powers(subset_analyzed, fs=fs, nperseg=nperseg, freq_range=freq_range)
power_outputs = shared.add_mean_and_std(power_outputs)
```


```{python plot_trials_welch, use_rave = FALSE, deps = "power_outputs"}
individual_trials = False
shared.plot_trials(power_outputs, individual_trials=individual_trials)
```




```{python fit_fooof_on_average, use_rave = FALSE, deps = c("power_outputs", "freq_range", "max_n_peaks")}
filtered_frequency = power_outputs['filtered_frequency']
average_power = power_outputs['Average Power']
title = None
freq_range = freq_range
max_n_peaks = max_n_peaks
aperiodic_mode = 'fixed'
plt_log = False
shared.fit_fooof(filtered_frequency, average_power, title=title, freq_range=freq_range, max_n_peaks=max_n_peaks, aperiodic_mode=aperiodic_mode, plt_log=plt_log)
```


Tuning coming next!!!

Tuning max_n_peaks

```{python tune_max_n_peaks, use_rave = FALSE, deps = "power_outputs"}
freq_range = [1, 175]
aperiodic_mode='fixed'
peaks_range = shared.np.arange(9)


filtered_freqs = power_outputs['filtered_frequency']
filtered_powers = power_outputs['Average Power']


shared.tune_max_n_peaks(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, aperiodic_mode=aperiodic_mode, peaks_range=peaks_range)

```



Tuning aperiodic_mode

```{python tune_aperiodic_mode, use_rave = FALSE, deps = "power_outputs"}
filtered_freqs = power_outputs['filtered_frequency']
filtered_powers = power_outputs['Average Power']
freq_range = [1, 175]
max_n_peaks=4


shared.tune_aperiodic_mode(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, max_n_peaks=max_n_peaks, show_errors=True)

```



Tuning peak_threshold

```{python tune_peak_threshold, use_rave = FALSE, deps = "power_outputs"}
freq_range = [1, 175]
max_n_peaks=4
aperiodic_mode="knee"
peak_threshold_range = shared.np.logspace(start = 0, stop = 1, num = 100)

filtered_freqs = power_outputs['filtered_frequency']
filtered_powers = power_outputs['Average Power']

shared.tune_peak_threshold(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, max_n_peaks=max_n_peaks, aperiodic_mode=aperiodic_mode, peak_threshold_range=peak_threshold_range, show_errors=True)

```















<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fooof_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fooof_module.R")
```


Once the pipeline script `make-fooof_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```






