---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("fooof_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->

Load data

```{r load_rave_subject, use_rave = TRUE, export = "subject", format = "rave-subject"}
subject = raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

```{r load_rave_repository, use_rave = TRUE, export = "repository", format = "rave_prepare_subject_voltage_with_epoch"}
repository = raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = channels_to_load,
  epoch_name = epoch_name,
  reference_name = reference_name,
  time_windows = time_window_to_load,
)
```

```{r prepare_data_for_fooof, use_rave = TRUE, export = "data_for_fooof"}
data_for_fooof = list(
  sample_rate = repository$subject$raw_sample_rates,
  electrodes = repository$electrode_list,
  analyze_channel = analyze_channel,
  epoch_table = repository$epoch_table,
  condition_groupings = unname(condition_groupings),
  voltage = repository$voltage$data_list[[sprintf("e_%d", analyze_channel)]]
)
```


```{r prepare_trial_subset, use_rave = TRUE, export = "subset_analyzed"}
conditions_analyzed = c("drive_a", "meant_a")

trial_selection = repository$epoch_table$Condition %in% conditions_analyzed
sub_volt = subset(repository$voltage$data_list$e_14, Trial ~ trial_selection)

matrix_volt = apply(sub_volt, c(1, 2), mean)
# matrix_volt


# Convert the matrix to a dataframe
df_volt = as.data.frame(matrix_volt)

# Setting column names for trials as they appear in the original array
colnames(df_volt) <- dimnames(sub_volt)$Trial

# Adding Time as a new column in the dataframe
df_volt$Time <- as.numeric(dimnames(sub_volt)$Time)

# Rearranging the dataframe to have Time as the first column
subset_analyzed <- df_volt[c("Time", dimnames(sub_volt)$Trial)]
```

```{python}
subset_analyzed = r.subset_analyzed

```

```{python generate_power_outputs, use_rave = TRUE, export = "power_outputs"}
power_outputs = shared.pd.DataFrame()
freqs = shared.pd.DataFrame()

# Parameters for preprocessing (you should adjust these based on your actual requirements)
fs = 2000
nperseg = 4000
freq_range = [1, 175]


# Loop through each column in the original dataframe
freq_in = False
for column in subset_analyzed.columns[1:]:
    # Apply the preprocess function to each column
    # subset_analyzed[column].values to pass the column data as an array
    filtered_freqs, filtered_powers = shared.preprocess_data(subset_analyzed[column].values, frequency=fs, freq_range=freq_range, nperseg=nperseg)

    # Create a new column name based on the original column name
    new_column_name = f"Trial_{column}_power"

    # Add the processed power data to the new dataframe
    if not freq_in:
        power_outputs["filtered_frequency"] = filtered_freqs
        freq_in = True
    power_outputs[new_column_name] = filtered_powers
    freqs[new_column_name] = filtered_freqs

# power_outputs.columns
power_outputs = shared.add_mean_and_std(power_outputs)
# power_outputs
```


```{python}
individual_trials = False
shared.plot_trials(power_outputs, individual_trials=individual_trials)
```


```{python}
filtered_frequency = power_outputs['filtered_frequency']
average_power = power_outputs['Average Power']
shared.fit_fooof(filtered_frequency, average_power)
```


Tuning coming next!!!

Tuning max_n_peaks

```{python}
filtered_freqs = filtered_frequency
filtered_powers = average_power
freq_range = [1, 175]
aperiodic_mode='fixed'
peaks_range = shared.np.arange(9)


shared.tune_max_n_peaks(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, aperiodic_mode=aperiodic_mode, peaks_range=peaks_range)
```



Tuning aperiodic_mode

```{python}
filtered_freqs = filtered_frequency
filtered_powers = average_power
freq_range = [1, 175]
max_n_peaks=4


shared.tune_aperiodic_mode(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, max_n_peaks=max_n_peaks, show_errors=True)

```



Tuning peak_threshold

```{python}
filtered_freqs = filtered_frequency
filtered_powers = average_power
freq_range = [1, 175]
max_n_peaks=4
aperiodic_mode="knee"
peak_threshold_range = shared.np.logspace(start = 0, stop = 1, num = 100)

shared.tune_peak_threshold(filtered_freqs=filtered_freqs, filtered_powers=filtered_powers, freq_range=freq_range, max_n_peaks=max_n_peaks, aperiodic_mode=aperiodic_mode, peak_threshold_range=peak_threshold_range, show_errors=True)

```

















Calculate the correlation coefficients

```{python}
data_for_fooof = r.data_for_fooof
data_for_fooof
```




```{python}
first_row_data = data_for_fooof['voltage'][0]
# first_row_data
fs = 2000
nperseg = 4000
freq_range = [1, 175]

max_n_peaks = 3
aperiodic_mode = "fixed"
plt_log = False
report = True

filtered_freqs, filtered_powers = shared.preprocess_data(first_row_data, fs, freq_range, nperseg)
# filtered_freqs
shared.generate_model_fit(filtered_freqs, filtered_powers, freq_range = freq_range, max_n_peaks = max_n_peaks, aperiodic_mode = aperiodic_mode, plt_log = plt_log, report = report)

# plt.plot(np.arrange(0, len(first_row_data) / fs, 1/fs), first_row_data)
```


```{python}
max_n_peaks = 10000
aperiodic_mode = "fixed"
plt_log = False
report = False

first_row_data = data_for_fooof['voltage'][0]
first_row_data
fs = 200
nperseg = 20
freq_range = [1, 175]
filtered_freqs, filtered_powers = shared.preprocess_data(first_row_data, fs, freq_range, nperseg)
filtered_freqs
filtered_powers

fm = shared.SpectralModel(max_n_peaks = max_n_peaks, aperiodic_mode = aperiodic_mode)
fm.fit(filtered_freqs, filtered_powers, freq_range)
fm.plot(plt_log = plt_log)
shared.plt.show()
```



```{r}
raveio::prep
```



```{python}
electrode = '14'
block = '11'
frequency = 2000
length = 0.1
timestamp = 0
_ = shared.extract_data(electrode, block, frequency, timestamp, length, plot=True)

length = 1.5
_ = extract_data(electrode, block, frequency, timestamp, length, plot=True)
```







```{python calculate_correlation, use_rave = TRUE, deps = "data_for_fooof", export = "correlation"}
correlation = shared.fooof_function1(data_for_fooof)
```

<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fooof_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fooof_module.R")
```


Once the pipeline script `make-fooof_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```






