---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("fooof_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->

Load data

```{rave load_rave_subject, use_rave = TRUE, export = "subject", format = "rave-subject"}
subject = raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

```{rave load_rave_repository, use_rave = TRUE, export = "repository", format = "rave_prepare_subject_voltage_with_epoch", cue = "always"}
repository = raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = channels_to_load,
  epoch_name = epoch_name,
  reference_name = reference_name,
  time_windows = time_window_to_load,
)
```

```{rave get_data_sampling_rate, use_rate = TRUE, export = "sample_rate"}
sample_rate <- repository$subject$raw_sample_rates[[1]]
```

```{rave prepare_data_for_fooof, use_rave = TRUE, deps = "repository", export = "data_for_fooof"}
data_for_fooof = list(
  sample_rate = repository$subject$raw_sample_rates,
  electrodes = repository$electrode_list,
  analyze_channel = analyze_channel,
  epoch_table = repository$epoch_table,
  condition_groupings = unname(condition_groupings),
  voltage = repository$voltage$data_list[[sprintf("e_%d", analyze_channel)]]
)
```

```{rave prepare_trial_subset, use_rave = TRUE, deps = c("repository", "condition_groupings"), export = "subset_analyzed"}
process_data <- function(repository, conditions_analyzed) {
  # Apply the condition to filter rows
  trial_selection <- repository$epoch_table$Condition %in% conditions_analyzed
  sub_volt <- subset(repository$voltage$data_list$e_14, Trial ~ trial_selection)

  # Calculate the mean across the first two dimensions
  matrix_volt <- apply(sub_volt, c(1, 2), mean)

  # Convert the matrix to a dataframe
  df_volt <- as.data.frame(matrix_volt)

  # Set column names for trials as they appear in the original array
  colnames(df_volt) <- dimnames(sub_volt)$Trial

  # Add 'Time' as a new column in the dataframe
  df_volt$Time <- as.numeric(dimnames(sub_volt)$Time)

  # Rearrange the dataframe to have 'Time' as the first column
  subset_analyzed <- df_volt[c("Time", dimnames(sub_volt)$Trial)]

  # Return the processed DataFrame
  return(subset_analyzed)
}
condition_keys <- names(condition_groupings)
conditions_analyzed <- lapply(condition_keys, function(key)
  condition_groupings[[key]][['conditions']])
# names(conditions_analyzed) <- paste0("subset_analyzed_", condition_keys)
# subset_analyzed <- process_data(repository=repository, conditions_analyzed=conditions_analyzed[[3]])
subset_analyzed <- lapply(conditions_analyzed, function(conditions) {
  process_data(repository, conditions)
})


```


```{r}
# repository$voltage$data_list$e_14
```

```{rave give_conditions_analyzed, use_rave = TRUE, deps = "condition_groupings", export = "conditions_analyzed_1"}
condition_keys <- names(condition_groupings)
conditions_analyzed_1 <- lapply(condition_keys, function(key)
  condition_groupings[[key]][['label']])
```



```{python}
conditions_analyzed_1 = r.conditions_analyzed_1
subset_analyzed = r.subset_analyzed
sample_rate = r.sample_rate
standard_deviation = r.standard_deviation
window_length = r.window_length
freq_range = r.freq_range
max_n_peaks = r.max_n_peaks
aperiodic_mode = r.aperiodic_mode
freq_range_aperiodic_tuning = r.freq_range_aperiodic_tuning
max_n_peaks_aperiodic_tuning = r.max_n_peaks_aperiodic_tuning
freq_range_tuning_max_n_peaks = r.freq_range_tuning_max_n_peaks
aperiodic_mode_tuning_max_n_peaks = r.aperiodic_mode_tuning_max_n_peaks
peaks_range_tuning_max_n_peaks = r. peaks_range_tuning_max_n_peaks
freq_range_tuning_peak_threshold = r.freq_range_tuning_peak_threshold
max_n_peaks_tuning_peak_threshold = r.max_n_peaks_tuning_peak_threshold
aperiodic_mode_tuning_peak_threshold = r.aperiodic_mode_tuning_peak_threshold
threshold_value_range_tuning_peak_threshold = r.threshold_value_range_tuning_peak_threshold
number_of_threshold_value_tuning_peak_threshold = r.number_of_threshold_value_tuning_peak_threshold
```


```{python generate_power_outputs, use_rave = TRUE, deps = c("subset_analyzed", "sample_rate", "window_length", "freq_range"), export = "power_outputs_list"}
# Parameters for preprocessing (you should adjust these based on your actual requirements)
fs = sample_rate

# Number of timepoints = sample rate * window size in sec
nperseg = sample_rate * window_length

freq_range = freq_range
power_outputs_list = []
for i in range(0, len(subset_analyzed)):
  power_outputs = shared.preprocess_powers(subset_analyzed[i], fs=fs, nperseg=nperseg, freq_range=freq_range)
  power_outputs = shared.add_mean_and_std(power_outputs)
  power_outputs_list.append(power_outputs)
```


```{python extract_one_power_output, use_rave = TRUE, deps = "power_outputs_list", export = "power_outputs"}
power_outputs = power_outputs_list[0]
```


```{python plot_trials_welch, use_rave = FALSE, deps = "power_outputs_list"}
individual_trials = False
shared.plot_trials(power_outputs_list, individual_trials=individual_trials)
```




```{python fit_fooof_on_average, use_rave = TRUE, deps = c("power_outputs", "max_n_peaks", "aperiodic_mode", "freq_range"), export = "fitted_fooof", cue = "always"}
filtered_frequency = power_outputs['filtered_frequency']
average_power = power_outputs['Average Power']
# title = None
# freq_range = freq_range
# plt_log = False
# aperiodic_mode = 'fixed'
fitted_fooof = shared.fit_fooof(
  filtered_freqs = filtered_frequency, 
  filtered_powers = average_power, 
  freq_range = freq_range,
  max_n_peaks=max_n_peaks, 
  aperiodic_mode=aperiodic_mode
)
```


```{python plot_fooof_fit, use_rave = FALSE, deps = c("power_outputs_list", "max_n_peaks", "aperiodic_mode", "freq_range", "conditions_analyzed_1")}
# title = None
freq_range = freq_range
max_n_peaks=max_n_peaks
plt_log = True
aperiodic_mode = aperiodic_mode
shared.plot_fooof_fits(
  power_outputs_list,
  freq_range,
  max_n_peaks, 
  aperiodic_mode,
  conditions_analyzed_1,
  plt_log=plt_log,
)
```


Tuning coming next!!!

Tuning max_n_peaks

```{python tune_max_n_peaks, use_rave = FALSE, deps = c("power_outputs_list", "freq_range_tuning_max_n_peaks", "aperiodic_mode_tuning_max_n_peaks", "peaks_range_tuning_max_n_peaks")}
freq_range = freq_range_tuning_max_n_peaks
aperiodic_mode=aperiodic_mode_tuning_max_n_peaks
peaks_range = peaks_range_tuning_max_n_peaks

shared.tune_max_n_peaks(power_outputs_list, freq_range=freq_range, aperiodic_mode=aperiodic_mode, peaks_range=peaks_range)
```



Tuning aperiodic_mode

```{python tune_aperiodic_mode, use_rave = FALSE, deps = c("power_outputs_list", "freq_range_aperiodic_tuning", "max_n_peaks_aperiodic_tuning")}

freq_range = freq_range_aperiodic_tuning
max_n_peaks = max_n_peaks_aperiodic_tuning

shared.tune_aperiodic_mode(power_outputs_list, freq_range=freq_range, max_n_peaks=max_n_peaks, show_errors=True)

```



Tuning peak_threshold

```{python tune_peak_threshold, use_rave = FALSE, deps = c("power_outputs_list", "freq_range_tuning_peak_threshold", "max_n_peaks_tuning_peak_threshold", "aperiodic_mode_tuning_peak_threshold", "threshold_value_range_tuning_peak_threshold", "number_of_threshold_value_tuning_peak_threshold")}
freq_range=freq_range_tuning_peak_threshold
max_n_peaks=max_n_peaks_tuning_peak_threshold
aperiodic_mode=aperiodic_mode_tuning_peak_threshold
start1=threshold_value_range_tuning_peak_threshold[0]
stop1=threshold_value_range_tuning_peak_threshold[1]
num1=number_of_threshold_value_tuning_peak_threshold

shared.tune_peak_threshold(power_outputs_list, freq_range=freq_range, max_n_peaks=max_n_peaks, aperiodic_mode=aperiodic_mode, start1=start1, stop1=stop1, num1=num1, show_errors=True)

```















<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fooof_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fooof_module.R")
```


Once the pipeline script `make-fooof_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```






