---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("fooof_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->

Load data

```{rave load_rave_subject, use_rave = TRUE, export = "subject", format = "rave-subject"}
subject = raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

```{rave load_rave_repository, use_rave = TRUE, export = "repository", format = "rave_prepare_subject_voltage_with_epoch"}
repository = raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = channels_to_load,
  epoch_name = epoch_name,
  reference_name = reference_name,
  time_windows = time_window_to_load,
)
```


```{rave prepare_data_for_fooof, use_rave = TRUE, export = "data_for_fooof"}
data_for_fooof = list(
  sample_rate = repository$subject$raw_sample_rates,
  electrodes = repository$electrode_list,
  analyze_channel = analyze_channel,
  epoch_table = repository$epoch_table,
  condition_groupings = unname(condition_groupings),
  voltage = repository$voltage$data_list[[sprintf("e_%d", analyze_channel)]]
)
```


```{rave prepare_trial_subset, use_rave = TRUE, export = "subset_analyzed"}
conditions_analyzed = c("drive_a", "meant_a")

trial_selection = repository$epoch_table$Condition %in% conditions_analyzed
sub_volt = subset(repository$voltage$data_list$e_14, Trial ~ trial_selection)

matrix_volt = apply(sub_volt, c(1, 2), mean)
# matrix_volt


# Convert the matrix to a dataframe
df_volt = as.data.frame(matrix_volt)

# Setting column names for trials as they appear in the original array
colnames(df_volt) <- dimnames(sub_volt)$Trial

# Adding Time as a new column in the dataframe
df_volt$Time <- as.numeric(dimnames(sub_volt)$Time)

# Rearranging the dataframe to have Time as the first column
subset_analyzed <- df_volt[c("Time", dimnames(sub_volt)$Trial)]
```

```{python}
subset_analyzed = r.subset_analyzed

```

```{python generate_power_outputs, use_rave = TRUE, export = "power_outputs", deps = c("subset_analyzed")}
power_outputs = shared.pd.DataFrame()
freqs = shared.pd.DataFrame()

# Parameters for preprocessing (you should adjust these based on your actual requirements)
fs = 2000
nperseg = 4000
freq_range = [1, 175]


# Loop through each column in the original dataframe
freq_in = False
for column in subset_analyzed.columns[1:]:
    # Apply the preprocess function to each column
    # subset_analyzed[column].values to pass the column data as an array
    filtered_freqs, filtered_powers = shared.preprocess_data(subset_analyzed[column].values, frequency=fs, freq_range=freq_range, nperseg=nperseg)
    
    # Create a new column name based on the original column name
    new_column_name = f"Trial_{column}_power"
    
    # Add the processed power data to the new dataframe
    if not freq_in:
        power_outputs["filtered_frequency"] = filtered_freqs
        freq_in = True
    power_outputs[new_column_name] = filtered_powers
    freqs[new_column_name] = filtered_freqs
  
# power_outputs.columns
power_outputs = shared.add_mean_and_std(power_outputs)
# power_outputs
```





<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fooof_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fooof_module.R")
```


Once the pipeline script `make-fooof_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```






